%-------------------------
% Resume in LaTeX
% Author: Neil Thomas
% Based on: https://github.com/sb2nov/resume
% https://github.com/jakegut/resume
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{lmodern}
\usepackage{fancyhdr}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{xcolor}



\usepackage{marvosym}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage[colorlinks=true,
            urlcolor=myblue,
            linkcolor=black,
            citecolor=black]{hyperref}

\pagecolor{white}
\definecolor{myblue}{HTML}{3399FF}


%----------FONT OPTIONS----------
% (commented out alternates)

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}


\usepackage[letterpaper, top=0.6in, bottom=0.6in, left=0.3in, right=0.3in]{geometry}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\bfseries\scshape\raggedright\small
}{}{0em}{}[\vspace{-7pt}\color{black}\rule{\linewidth}{0.7pt}\vspace{-7pt}]



% Ensure ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\educationSection}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textit{\small #4} \\[-2pt]
      {\small #3} & {\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \textit{\small #4} \\[-2pt]
      \textbf{\small #3} & {\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\normalsize$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\vspace*{-1.5cm}
\begin{center}
    \textbf{\LARGE \scshape Leonardo da Vinci} \\ \vspace{4pt}
    \small \href{mailto:leonardo@renaissance.it}{+39 555 123 4567} $|$
    \href{mailto:leonardo@renaissance.it}{leonardo@renaissance.it} $|$
    \href{https://linkedin.com/in/leodavinci}{\underline{linkedin.com/in/leodavinci}} $|$
    \href{https://github.com/leodavinci}{\underline{github.com/leodavinci}} $|$
    \href{https://leodavinci.art}{\underline{leodavinci.art}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \educationSection
      {Verrocchio’s Workshop}{1469 -- 1476}
      {Apprenticeship in Painting, Sculpture, Mechanics, Architecture}{Florence, Italy}
    \educationSection
      {Self-Directed Study}{1476 -- 1519}
      {Anatomy, Geometry, Engineering, Physics, Astronomy, Hydrodynamics}{Florence, Italy}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Court Engineer and Artist}{1482 -- 1499}
      {Duke Ludovico Sforza}{Milan, Italy}
      \resumeItemListStart
        \resumeItem{Designed large-scale fortifications, urban infrastructure, and innovative canal systems while conceptualizing advanced machinery such as tanks, flying devices, and hydraulic engines.}
        \resumeItem{Painted \href{https://en.wikipedia.org/wiki/The_Last_Supper_(Leonardo)}{\textbf{The Last Supper}}, applying anatomy, mathematics, and optics to create revolutionary perspective and emotional resonance.}
        \resumeItem{Drafted visionary proposals for Milanese city planning and agriculture that merged architecture, hydraulics, and civic engineering into cohesive blueprints.}
        \resumeItem{Advised the court on military, architectural, and cultural innovation, elevating Milan’s reputation as a Renaissance capital.}
      \resumeItemListEnd

    \resumeSubheading
      {Architect and Military Engineer}{1502 -- 1503}
      {Cesare Borgia}{Central Italy}
      \resumeItemListStart
        \resumeItem{Conducted topographic surveys and created highly accurate maps that fused mathematical projection with artistic rendering.}
        \resumeItem{Designed advanced siege engines, mobile bridges, and artillery improvements to give Borgia’s forces technological advantages.}
      \resumeItemListEnd

    \resumeSubheading
      {Artist and Inventor}{1503 -- 1519}
      {Independent}{Florence, Milan, Rome, Amboise}
      \resumeItemListStart
        \resumeItem{Painted \href{https://en.wikipedia.org/wiki/Mona_Lisa}{\textbf{Mona Lisa}}, pioneering sfumato blending and psychological realism to transform portraiture into a study of human depth.}
        \resumeItem{Performed dissections of 30+ cadavers, producing anatomical sketches that anticipated modern medical diagrams.}
        \resumeItem{Invented hydraulic pumps, robotic devices, and flying machines, filling \textbf{13,000+ notebook pages} with designs bridging science and art.}
        \resumeItem{Worked under patrons such as Pope Leo X and King Francis I, producing works across art, science, engineering, and philosophy.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\vspace{-4mm}
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\href{https://en.wikipedia.org/wiki/Codex_Atlanticus}{\textbf{Codex Atlanticus}} $|$ \emph{Engineering, Mathematics, Physics}}{}
      \resumeItemListStart
        \resumeItem{Compiled extensive notebooks on hydraulics, mechanics, aerodynamics, architecture, and weaponry, providing a window into Renaissance scientific inquiry.}
        \resumeItem{Outlined designs for helicopters, tanks, diving suits, and calculators, centuries ahead of material feasibility.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\href{https://en.wikipedia.org/wiki/Leonardo_da_Vinci\%27s_anatomical_studies}{\textbf{Anatomical Drawings}} $|$ \emph{Biology, Medicine, Illustration}}{}
      \resumeItemListStart
        \resumeItem{Dissected cadavers and produced highly accurate sketches of the circulatory system, muscular structure, and skeletal framework.}
        \resumeItem{Created anatomical illustrations that united observational science with artistic mastery, influencing medicine and art for generations.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\vspace{-4mm}
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Languages:} Italian, Latin, French \\
    \textbf{Artistic:} Oil Painting, Fresco, Drawing, Sculpture, Perspective, Sfumato, Chiaroscuro \\
    \textbf{Engineering:} Hydraulics, Mechanics, Architecture, Optics, Cartography, Anatomy, Astronomy \\
    \textbf{Inventions:} Flying Machines, War Engines, Hydraulic Pumps, Robotics, Architectural Models \\
    \textbf{Tools:} Paintbrush, Chisel, Compass, Caliper, Quill, Notebook \\
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
